The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-08-09 paper/paper.Rmd
ran styler

# knitr settings
opts_chunk$set(
  # Code output:
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  cache = TRUE,
  # Figure:
  out.width = "100%",
  fig.path = "Figures/",
  fig.width = 16 / 2.5,
  fig.height = 9 / 2.5,
  fig.align = "center",
  fig.show = "hold",
  # Etc:
  collapse = TRUE,
  comment = "##",
  tidy.opts = list(width.cutoff=72),
  tidy = TRUE
)

@@

```{r scbi-load-data}
census_2013_scbi <- read_csv("scbi.stem2.csv") %>%
  select(stemID, sp, date = ExactDate, gx, gy, dbh, codes, status) %>%
  mutate(
    # Convert date from character to date
    date = mdy(date),
    # Convert dbh to be in cm
    dbh = as.numeric(dbh)/10
  ) %>%
  filter(gx < 300, between(gy, 300, 600))

census_2018_scbi <- read_csv("scbi.stem3.csv") %>%
  select(stemID, sp, date = ExactDate, gx, gy, dbh, codes, status) %>%
  mutate(
    date = mdy(date),
    dbh = as.numeric(dbh)/10
  ) %>%
  filter(gx < 300, between(gy, 300, 600))
```

@@

```{r scbi-spatial-information, out.width="66%", fig.cap="Step 2 - Add spatial information. A buffer region and spatial cross-validation blocks 1 through 4. The location of each tree is marked with its fold number where the folds are delineated with solid lines. The color of each digit indicates whether the tree is part of the buffer region (thus will only be considered as a competitor tree) or is part of the interior of the study region (thus is a focal tree whose growth is of modeled interest)."}
ggplot() +
  geom_sf(data = blocks_scbi, fill = "transparent", linetype = "dashed") +
  geom_sf_text(data = growth_scbi %>% sample_n(1000), 
               aes(label = foldID, col = buffer))
```

@@

```{r scbi-model-predict}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  mutate(growth_hat = predict(comp_bayes_lm_scbi, 
                              newdata = focal_vs_comp_scbi))
```
```{r show-focal-vs-comp}
focal_vs_comp_scbi %>% 
  select(focal_ID, focal_sp, dbh, growth, growth_hat)
```

@@

plot1 <- autoplot(comp_bayes_lm_scbi, type = "intercepts", 
                  sp_to_plot = sp_to_plot)
plot2 <- autoplot(comp_bayes_lm_scbi, type = "dbh_slopes", 
                  sp_to_plot = sp_to_plot)
plot3 <- autoplot(comp_bayes_lm_scbi, type = "competition", 
                  sp_to_plot = sp_to_plot)

@@

focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  mutate(growth_hat_shuffle = predict(comp_bayes_lm_scbi_shuffle, 
                                 newdata = focal_vs_comp_scbi))
```
```{r show-rmse-shuffle}
model_rmse_shuffle <- focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat_shuffle) %>%
  pull(.estimate)
model_rmse_shuffle
```

>>>>

# knitr settings
opts_chunk$set(
  # Code output:
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  cache = TRUE,
  # Figure:
  out.width = "100%",
  fig.path = "Figures/",
  fig.width = 16 / 2.5,
  fig.height = 9 / 2.5,
  fig.align = "center",
  fig.show = "hold",
  # Etc:
  collapse = TRUE,
  comment = "##",
  tidy.opts = list(width.cutoff = 72),
  tidy = TRUE
)

@@

```{r scbi-load-data}
census_2013_scbi <- read_csv("scbi.stem2.csv") %>%
  select(stemID, sp, date = ExactDate, gx, gy, dbh, codes, status) %>%
  mutate(
    # Convert date from character to date
    date = mdy(date),
    # Convert dbh to be in cm
    dbh = as.numeric(dbh) / 10
  ) %>%
  filter(gx < 300, between(gy, 300, 600))

census_2018_scbi <- read_csv("scbi.stem3.csv") %>%
  select(stemID, sp, date = ExactDate, gx, gy, dbh, codes, status) %>%
  mutate(
    date = mdy(date),
    dbh = as.numeric(dbh) / 10
  ) %>%
  filter(gx < 300, between(gy, 300, 600))
```

@@

```{r scbi-spatial-information, out.width="66%", fig.cap="Step 2 - Add spatial information. A buffer region and spatial cross-validation blocks 1 through 4. The location of each tree is marked with its fold number where the folds are delineated with solid lines. The color of each digit indicates whether the tree is part of the buffer region (thus will only be considered as a competitor tree) or is part of the interior of the study region (thus is a focal tree whose growth is of modeled interest)."}
ggplot() +
  geom_sf(data = blocks_scbi, fill = "transparent", linetype = "dashed") +
  geom_sf_text(
    data = growth_scbi %>% sample_n(1000),
    aes(label = foldID, col = buffer)
  )
```

@@

```{r scbi-model-predict}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  mutate(growth_hat = predict(comp_bayes_lm_scbi,
    newdata = focal_vs_comp_scbi
  ))
```
```{r show-focal-vs-comp}
focal_vs_comp_scbi %>%
  select(focal_ID, focal_sp, dbh, growth, growth_hat)
```

@@

plot1 <- autoplot(comp_bayes_lm_scbi,
  type = "intercepts",
  sp_to_plot = sp_to_plot
)
plot2 <- autoplot(comp_bayes_lm_scbi,
  type = "dbh_slopes",
  sp_to_plot = sp_to_plot
)
plot3 <- autoplot(comp_bayes_lm_scbi,
  type = "competition",
  sp_to_plot = sp_to_plot
)

@@

focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  mutate(growth_hat_shuffle = predict(comp_bayes_lm_scbi_shuffle,
    newdata = focal_vs_comp_scbi
  ))
```
```{r show-rmse-shuffle}
model_rmse_shuffle <- focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat_shuffle) %>%
  pull(.estimate)
model_rmse_shuffle
```
